SunPy - Python for Solar Physics

### 2014-01-28 3-5-Database.tex
changed code example in database subsection

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.net import vso
>>> from sunpy.database import Database
>>> database = Database('sqlite:///')
>>> database.download(
...     vso.attrs.Time((2011, 9, 20, 1), (2011, 9, 20, 2)),
...     vso.attrs.Instrument('RHESSI'))
>>> len(database)
6
>>> from sunpy.database.tables import display_entries
>>> print display_entries(
...     database,
...     ['id', 'observation_time_start', 'wavemin', 'wavemax'])
id observation_time_start wavemin        wavemax    
-- ---------------------- -------        -------    
1  2011-09-20 01:09:20    0.413280643067 7.29318781883e-05

\end{minted}
\caption{Example usage of the database sub-package.}
\label{code:database}
\end{listing}

>>>>

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.net import vso
>>> from sunpy.database import Database
>>> database = Database('sqlite:///')
>>> database.download(
...     vso.attrs.Time('2012-08-05', '2012-08-05 00:00:05'),
...     vso.attrs.Instrument('AIA'))
>>> len(database)
2
>>> from sunpy.database.tables import display_entries
>>> print display_entries(
...     database,
...     ['id', 'observation_time_start', 'wavemin', 'wavemax'])
id observation_time_start wavemin wavemax
-- ---------------------- ------- -------
1  2012-08-05 00:00:01    9.4     9.4    
2  2012-08-05 00:00:02    33.5    33.5   
\end{minted}
\caption{Example usage of the database sub-package.}
\label{code:database}
\end{listing}
